---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Wage Gaps Thesis"
#subtitle: "This will appear as Right Header"


documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Emma Terblanche"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University" # First Author's Affiliation
Email1: "21777039\\@sun.ac.za" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Wage Gaps \\sep South Africa \\sep Race" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
#Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
#  Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Packages
if(!require("tidyverse")) install.packages("tidyverse")
library(stargazer)
library(modelsummary)
library(broom)
library(knitr)

# Data
appendedGHS <- read.csv("/Users/mac/Desktop/Masters/Thesis Datawork/MincerRegRMD/data/appendedGHS.csv")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction


# Research Question 


# Literature Review 


# Data 


# Methodology 

\newpage 

# Results

```{r}
mincer2 <- lm(logsal ~ Race + prispline + secspline + terspline + AgeSq + Age + Gender + Race*Y2005 + Race*Y2009 + Race*Y2013 + Race*Y2016, data = appendedGHS)

```


```{r, fig.height = 3, results='asis'}
mincer3 <- lm(logsal ~ Race + prispline + secspline + terspline + exp + expsq + Gender + Race*Y2005 + Race*Y2009 + Race*Y2013 + Race*Y2016, data = appendedGHS)

stargazer(mincer2, mincer3,
          type = 'latex',
          
          title = "Mincer Regressions",
 
          header=FALSE, # to get rid of r package output text

          single.row = TRUE, # to put coefficients and standard errors on same line

          no.space = TRUE, # to remove the spaces after each line of coefficients

          column.sep.width = "3pt", # to reduce column width

          font.size = "small" # to make font size smaller

)
```

# 2002, 2005, 2009, 2013, 2016 Results 
## Without Experience 
In 2002: 
- White South Africans earned 88% more than Black South Africans. 
- Indian/Asian South Africans earned 70% more. 
- Coloured South Africans earned 28.56% more. 

In 2005: 
- Black workers earned 20.4% more than in 2002. 
- Relative to Black workers, Coloured workers earned 0.04% less than in 2005 than in 2002. 
- The gap between Indian/Asian workers and Black workers decreases by 22.98% by 2005. 
- The gap between White and Black workers also decreased, but only by 10.06%

By 2009: 
- Relative to 2002, Black workers earned 67.24% more. 
- Coloured workers earned 4.46% more relative to Black workers in 2002. 
- The gap between Indian/Asian and Black wages continued to decrease but only by 14.25% between 2002 and 2009. 
- The White-Black wage gap also decreased by 13.43%

By 2013: 
- Black workers earned 67.36% more in 2013 than in 2002 (very similar to 2009 - wage growth stagnating?)
- Relative to Black workers in 2013, Coloured workers earned 15.42% less 
- The Indian/Asian-Black and White-Black wage gaps started to increase again in 2013 (106.78% and 70.10% respectively)

By 2016: 
- Relative to 2002, Black workers earned 93.27% more. 
- The Coloured-Black and White-Black wage gaps increased by 7.43% and 2.88% respectively.
- The Indian/Asian-Black wage gap decreased by 2.02%. 

## With Experience: 
Very similar. Same trends, except: 2005 Coloured-Black wage gap now increase by 0.28% instead of decrease. 


# 2002, 2009, 2016 Results
Without Experience: 
As shown by the positive coefficients on the race categories in the first regression column, Black South Africans had the lowest salary expectations of the race groups. White South Africans were likely to earn 90% more than Black South Africans. Indian/Asian South Africans earned just over 70% more, and Coloured South Africans earned 27.83% more. The wage gap between Black and Coloured workers increased slightly between 2002 and 2009 by 0.49%. It further increased by 0.79% by 2016. The gap between the salaries of Black workers and that of Indian/Asian and White workers decreased from 2002 to 2009 by 13.7% and 13.04% respectively. The narrowing of the gap between Black and Indian/Asian workers appear to have plateaued between 2009 and 2016. In this period, the reduction was much smaller at approximately 0.67%. The wage gap between Black and White workers increased slightly again after 2009 by 4.04%. 

NOTAS: 
- neem aan dis "percent" en nie "percentage points" nie. 
- lyk my iets (once off) het gebeur tussen 2002 en 2009 wat die gaps baie kleiner gemaak het. 
- Weer erger na 2009

With Experience: 
Very similar.


# Conclusion 

\hfill

<!-- hfill can be used to create a space, like here between text and table. -->


# Conclusion
<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

